SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-31 docs/questioning.tex
More work on policy enforcement

This approach is used to detect attacks that target web users.
When using a framework that implements
this approach, developers must define
specific security policies on the server side.
Then the policies are enforced either in the user's
browser at runtime or in a server-side proxy that intercepts
server responses. Policy enforcement is one of the two
approaches (the other is Securing Mashups) that is
used to prevent {\sc csrf} attacks.

@@

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
acts as a proxy on the server side (locus {\sc y}) to
parse the {\sc html} of server responses and identifies
scripts. Then, it rewrites them into safe equivalents
and protect the web user from exploitations
that are based on reported browser vulnerabilities.
{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
and the framework by {\it Phung et al.}~\cite{PSC09}
extend JavaScript with new primitive functions to
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place on the JavaScript engine of the browser (locus {\sc x}).
In this way, {\sc xxs} attacks that take advantage
functions like {\tt eval} and {\tt write} that are
used to assemble innocuous-looking parts into harmful
strings would fail. A critical issue regarding
the above frameworks is that they cannot
define policies that restrict the behavior of third-party
scripts introduced by script inclusion and {\tt iframe}
tags. For instance, consider a web page ({\tt foo.net})
that prints the value of the a query parameter ({\tt query})
from the page's {\sc url} in the web page's content
without escaping the value. A malicious user
can take advantage of this and inject an {\tt iframe}
into the page to steal the user's cookie and
send it via an image request to a web site
that he or she controls ({\tt malicious.com}).
This could be achieved by including the following
link to the malicious web site (or send it via phishing)
and induce the user to click on it:

@@

{\it WebJail}~\cite{VDDPJ11}, overcomes this issue
by containing the functionality of third-party scripts.

@@

  &   {\it Diglossia}~\cite{SMS13} & 3 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\

>>>>

This approach is used to detect attacks that target web users.
When using a framework that implements
this approach, developers must define
specific security policies on the server side.
Then the policies are enforced either in the user's
browser at runtime or in a server-side proxy that intercepts
server responses. Policy enforcement is one of the two
approaches (the other is Securing Mashups --- see
Subsubsection~\ref{sec:mashups}) that is
used to prevent {\sc csrf} attacks.

{\it Noxes}~\cite{KKVJ06,KJKV09} is the only
framework that partially allows the web
user to specify policies to prevent {\sc xss} attacks.
The key idea behind Noxes is to parse
the {\sc html} that reaches the browser to
find static {\sc url} references. Then, based on
a set of policies it allows or blocks
the request (locus {\sc x}). Such policies
are provided either by the user or by
the framework itself. Noxes does not
deal with JavaScript-driven {\sc xss}
attacks and it is a rather simplistic approach.

@@

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
acts as a proxy on the server side (locus {\sc y}) to
parse the {\sc html} of server responses and identifies
scripts. Then, it rewrites them into safe equivalents
and protect the web user from exploitations
that are based on reported browser vulnerabilities.
{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
and the framework by {\it Phung et al.}~\cite{PSC09}
extend JavaScript with new primitive functions to
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place on the JavaScript engine of the browser (locus {\sc x}).
In this way, {\sc xxs} attacks that take advantage
functions like {\tt eval} and {\tt write} that are
used to assemble innocuous-looking parts into harmful
strings would fail. A critical issue regarding
the above frameworks is that they cannot
define policies that restrict the behavior of third-party
scripts introduced by script inclusion and {\tt iframe}
tags. For instance, consider a web page ({\tt foo.net})
that prints the value of the a query parameter ({\tt query})
from the page's {\sc url} in the web page's content
without escaping the value. A malicious user
can take advantage of this and inject an {\tt iframe}
into the page to steal the user's cookie and
send it via an image request to a web site
that he or she controls ({\tt malicious.com}).
This could be achieved by including the following
link to the malicious web site (or send it via phishing
email) and induce the user to click on it:

@@

% {\it WebJail}~\cite{VDDPJ11}, overcomes this issue
% by containing the functionality of third-party scripts.

@@

  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
